Modal type theory based on the intuitionistic epistemic logic

### 2018-02-10 article.tex
added fixes

  \begin{itemize}
    \item $\text{fmap } \alpha_{\hat{A},\hat{B},\hat{C}} \circ \tau_{\hat{A} \times \hat{B}, \hat{C}} = \tau_{\hat{A}, \hat{B} \times \hat{C}} \circ (id_{\hat{A}} \times \tau_{\hat{B}, \hat{C}}) \circ \alpha_{\hat{A}, \hat{B}, {\bf K}\hat{C}}$;
    \item ${\bf K}(\rho_{\hat{A}}) \circ \tau_{\mathds{1}, \hat{A}} = \rho_{{\bf K}\hat{A}}$.
  \end{itemize}
  where $\alpha_{\hat{A},\hat{B},\hat{C}} = [p, \langle \pi_1 (\pi_1 p), \langle \pi_1 (\pi_2 p), \pi_2 p \rangle \rangle]$ and
  $\rho = \pi_2$.
\end{lemma}

@@

Simple, but routine checking.
\end{proof}

>>>>

  \begin{itemize}
    \item $\text{fmap } \alpha_{\hat{A},\hat{B},\hat{C}} \circ \tau_{\hat{A} \times \hat{B}, \hat{C}} = \tau_{\hat{A}, \hat{B} \times \hat{C}} \circ (id_{\hat{A}} \times \tau_{\hat{B}, \hat{C}}) \circ \alpha_{\hat{A}, \hat{B}, {\bf K}\hat{C}}$;
    \item ${\bf K}(\rho_{\hat{A}}) \circ \tau_{\mathds{1}, \hat{A}} = \rho_{{\bf K}\hat{A}}$.
  \end{itemize}
  where $\alpha_{\hat{A},\hat{B},\hat{C}} = [p, \langle \pi_1 (\pi_1 p), \langle \pi_2 (\pi_1 p), \pi_2 p \rangle \rangle]$ and
  $\rho = \pi_2$.
\end{lemma}

@@

1)

$\begin{array}{lll}
& \text{fmap } \alpha_{\hat{A},\hat{B},\hat{C}} \circ \tau_{\hat{A} \times \hat{B}, \hat{C}} = & \\
& [q, {\bf let \: pure \:} z = q {\: \bf in \:} \langle \pi_1 (\pi_1 z), \langle \pi_2 (\pi_1 z), \pi_2 z \rangle \rangle] \circ [p, {\bf let \: pure \:} x, y = {\bf pure \:}(\pi_1 p), \pi_2 {\: \bf in \:} \langle x, y \rangle ] = & \\
& [p, {\bf let \: pure \:} z = q {\: \bf in \:} \langle \pi_1 (\pi_1 z), \langle \pi_2 (\pi_1 z), \pi_2 z \rangle \rangle [q := {\bf let \: pure \:} x, y = {\bf pure \:}(\pi_1 p), \pi_2 {\: \bf in \:} \langle x, y \rangle]] = & \\
& [p, {\bf let \: pure \:} z = ({\bf let \: pure \:} x, y = {\bf pure \:}(\pi_1 p), \pi_2 {\: \bf in \:} \langle x, y \rangle) {\: \bf in \:} \langle \pi_1 (\pi_1 z), \langle \pi_2 (\pi_1 z), \pi_2 z \rangle \rangle] = & \\
& [p, {\bf let \: pure \:} x, y = {\bf pure \:}(\pi_1 p), \pi_2 {\: \bf in \:} \langle \pi_1 (\pi_1 z), \langle \pi_2 (\pi_1 z), \pi_2 z \rangle \rangle [z := x, y]] = & \\
& [p, {\bf let \: pure \:} x, y = {\bf pure \:}(\pi_1 p), \pi_2 {\: \bf in \:} \langle \pi_1 x, \langle \pi_2 x, y \rangle \rangle]&
\end{array}$
\end{proof}
